Make Database for Tableau Prototype

### 2020-03-10 sources/tools/make-tableau-data.Rmd
beta version functioning

# Overhead
```{r overhead, include = FALSE}
packages_vector <- c("tidyverse",
                     "jsonlite",
                     "visioneval")

@@

# import::here(ve.export,.from="./exporter.R")
```

@@

viewer_file_name <- paste0(viewer_dir,  "verspm.js")

scenario_config_file_name <- paste0(output_dir, "example_scenario_manage.csv")

@@

# Convert Javascript data to CSV
```{r convert-java}
temp_out_name <- paste0(output_dir, "verspm.JSON")
input  <- readLines(viewer_file_name)
  step_1 <- gsub(pattern = "var data =", replace = "", x = input)
  step_2 <- str_replace(step_1, ";", "")
  writeLines(step_2, con = temp_out_name)

temp_df <- fromJSON(temp_out_name, flatten = TRUE)

write_csv(temp_df, path = paste0(output_dir, "verspm.csv"))
```

# Prepare Tableau
```{r prep-tableau}
measure_names_vector <- c("GHGReduction", 
                          "DVMTPerCapita",
                          "WalkTravelPerCapita",
                          "TruckDelay",
                          "AirPollutionEm",
                          "FuelUse",
                          "VehicleCost",
                          "VehicleCostLow")

config_df <- read_csv(scenario_config_file_name, 
                      col_types = cols(.default = col_character(), execute = col_logical()))

category_name_dict_df <- distinct(config_df, category_name, category_label) %>%
  mutate(category_label = str_replace(category_label, " ", "_")) %>%
  select(short = category_name, long = category_label)

level_name_dict_df <- distinct(config_df, category_name, level_name, level_label)

outcomes_df <- read_csv(paste0(output_dir, "verspm.csv"),
                        col_types = cols(.default = col_character())) %>%
  mutate_at(vars(measure_names_vector), as.numeric)

@@

  level_dict_df <- level_name_dict_df %>%
    filter(category_name == category) %>%
    distinct(level_name, level_label)

@@

  working_df <- working_df %>%
    rename(subject := !!category) %>%
    left_join(., level_dict_df, by = c("subject" = "level_name")) %>%
    mutate(subject_copy = level_label) %>%
    rename(!!new_category_name := subject_copy) %>%
    rename(!!category := subject) %>%
    select(-level_label)

@@

  long_name <- filter(category_name_dict_df, short == category)$long

@@

  working_df <- working_df %>%
    rename(!!long_name := !!new_category_name) 
}

output_df <- working_df %>%
  mutate(scenario_index = row_number())

>>>>

# TODO: 
# make a vignette, 
# make a proper tool (in R)

# Overhead
```{r overhead, include = FALSE}
packages_vector <- c("tidyverse",
                     "jsonlite")

@@

@@

@@

# Private Methods
```{r methods}
.MakeDataframeFromJavaScript <- function(input_js_var_file_name, var_name_string) {

  temp_out_name <-  paste0(output_dir, "temp.JSON")
  input_line  <- readLines(input_js_var_file_name)
  step_1 <- stringr::str_replace(input_line, paste0("var ", var_name_string, " ="), "")
  step_2 <- stringr::str_replace(step_1, ";", "")
  writeLines(step_2, con = temp_out_name)

  return_df <- jsonlite::fromJSON(temp_out_name, simplifyVector = TRUE, flatten = TRUE)

  return(return_df)

.MakeScenarioDataframes <- function(input_scenario_dir, model_name = "verspm") {

  file_name <-  paste0(input_scenario_dir, model_name, ".js")
  results_df <- .MakeDataframeFromJavaScript(file_name, "data")

  file_name <-  paste0(input_scenario_dir, "output-cfg.js")
  output_config_df <- .MakeDataframeFromJavaScript(file_name, "outputcfg")

  file_name <-  paste0(input_scenario_dir, "scenario-cfg.js")
  scenario_config_df <- .MakeDataframeFromJavaScript(file_name, "scenconfig") %>%
    dplyr::rename(category_name = NAME, 
                  category_label = LABEL, 
                  category_description = DESCRIPTION,
                  category_instructions = INSTRUCTIONS) %>%
    tidyr::unnest(.,cols = c(category_name, category_label, category_description, 
                             category_instructions, LEVELS)) %>%
    dplyr::bind_cols(., tibble::tibble(level_name = unlist(.$NAME))) %>%
    dplyr::bind_cols(., tibble::tibble(level_label = unlist(.$LABEL))) %>%
    dplyr::bind_cols(., tibble::tibble(level_description = unlist(.$DESCRIPTION))) %>%
    dplyr::select(-NAME, -LABEL, -DESCRIPTION)

  file_name <-  paste0(input_scenario_dir, "category-cfg.js")
  category_config_df <- .MakeDataframeFromJavaScript(file_name, "catconfig") %>%
    dplyr::rename(strategy_label = NAME,
                  strategy_description = DESCRIPTION) %>%
    tidyr::unnest(., cols = c(strategy_label, strategy_description, LEVELS)) %>%
    dplyr::rename(strategy_bundle = NAME) %>%
    tidyr::unnest(., cols = c(strategy_bundle, INPUTS)) %>%
    dplyr::bind_cols(., tibble::tibble(category_name = unlist(.$NAME))) %>%
    dplyr::bind_cols(., tibble::tibble(level_name = unlist(.$LEVEL))) %>%
    dplyr::select(-LEVEL, -NAME)

  return_list <- list("results" = results_df,
                      "output_config" = output_config_df,
                      "scenario_config" = scenario_config_df,
                      "category_config" = category_config_df)

  return(return_list)
}

.notAllNA <- function(x) {

  return(any(!is.na(x)))

# Public Methods
```{r public-methods}
MakeTableauScenarioViewer <- function(input_scenario_dir,  model_name = "verspm") {

  df_list <- .MakeScenarioDataframes(input_scenario_dir, model_name)

  measure_names_vector <- df_list$output_config$COLUMN

  outcomes_df <- df_list$results %>%
    dplyr::mutate_at(dplyr::vars(all_of(measure_names_vector)), as.numeric)

  category_name_dict_df <- df_list$scenario_config %>%
    dplyr::distinct(category_name, category_label) %>%
    dplyr::mutate(category_label = stringr::str_replace_all(category_label, " ", "_")) %>%
    dplyr::select(short = category_name, long = category_label)

  level_name_dict_df <- df_list$scenario_config %>%
    dplyr::distinct(category_name, level_name, level_label)

@@

    level_dict_df <- level_name_dict_df %>%
      dplyr::filter(category_name == category) %>%
      dplyr::distinct(level_name, level_label)

@@

    working_df <- working_df %>%
      dplyr::rename(subject := !!category) %>%
      dplyr::left_join(., level_dict_df, by = c("subject" = "level_name")) %>%
      dplyr::mutate(subject_copy = level_label) %>%
      dplyr::rename(!!new_category_name := subject_copy) %>%
      dplyr::rename(!!category := subject) %>%
      dplyr::select(-level_label)

@@

    long_name <- dplyr::filter(category_name_dict_df, short == category)$long

@@

    working_df <- working_df %>%
      dplyr::rename(!!long_name := !!new_category_name) 
  }

  strategy_name_df <- df_list$category_config %>%
    tidyr::pivot_wider(., names_from = category_name, values_from = level_name)

  for (strategy in unique(strategy_name_df$strategy_label)) {

    join_df <- dplyr::filter(strategy_name_df, strategy_label == strategy) %>%
      dplyr::select(-strategy_description) %>%
      dplyr::select_if(.notAllNA)

    join_vector <- colnames(dplyr::select(join_df, -strategy_label, -strategy_bundle))

    strategy <- stringr::str_replace_all(strategy, " ", "_")
    strategy <- stringr::str_replace_all(strategy, "\\/", "_")
    strategy <- paste0("Strategy_", strategy)

    working_df <- dplyr::left_join(working_df, join_df, by = join_vector) %>%
      dplyr::rename(!!strategy := strategy_bundle) %>%
      dplyr::select(-strategy_label)

  return_df <- working_df %>%
    dplyr::mutate(scenario_index = dplyr::row_number())

  return(return_df)

}
```

# Apply Method
```{r apply-method}
output_df <- MakeTableauScenarioViewer(viewer_dir, model_name = "verspm")
```
